Enforced Invariant Confluence

### 2018-04-19 doc/paper/sections/related_work.tex
Finished first cut at related work.

\paragraph{Program Analysis in Database Systems}
TODO
% Program analysis in database:
%   look at some of alvins work and related stuff:
%   Find work on static partitioning of data based on program?
%   Transaction chopping / healing?

@@

>>>>

@@

\paragraph{Program Analysis in Database Systems}
Using program analysis to improve the performance of database systems is not
new. For example, it has been used to improve the performance of
database-backed web applications~\cite{cheung2014using, wu2016transaction,
ramachandra2012program} and used to improve the performance of optimistic
concurrency control on multi-core machines~\cite{wu2016transaction}. Our work
on invariant-confluence continues the theme of using program analysis to reap
the performance benefits of understanding program semantics that would
otherwise be left on the table.
